Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-08-24 pnas/Towards.tex
initial files for pnas

\documentclass[english,11pt]{article}

\pdfoutput=1

\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{color}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools} 
\usepackage[margin=1.2in]{geometry}
\usepackage{showlabels}

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}

\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}

\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}

\newcommand{\TODO}[1]{{\color{red}{[#1]}}}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
%\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

\newtheorem*{lem*}{Lemma}

\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{plain}
\newtheorem{corollary}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{proposition}[thm]{\protect\propositionname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\usepackage{slashbox}

\usepackage{babel}
\providecommand{\claimname}{Claim}
\providecommand{\definitionname}{Definition}
\providecommand{\lemmaname}{Lemma}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\corollaryname}{Corollary}
\providecommand{\propositionname}{Proposition}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\tamir}{x}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\RPP}{\mathbb{R}^{P\times P}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\hx}{\hat{x}} 
\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
\newcommand{\be}
{\begin{equation}}
\newcommand{\ee}
{\end{equation}}

@@

\author{Tamir Bendory, Nicolas Boumal, William Leeb, Eitan Levin and Amit Singer}
\maketitle

\begin{abstract}
	Here comes the abstract
\end{abstract}

\section{Introduction}

\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
% 
In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. Within the ice, the molecules are randomly oriented and positioned. The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}. Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions. The goal is to construct 3-D models of the molecules from the micrographs.

@@

%\paragraph{Particle picking.}
All contemporary methods in the field split the reconstruction procedure into several stages.
The first stage consists in extracting the various particle projections from the micrographs. This stage is called \emph{particle picking}. Later stages aim to construct a 3-D model of the molecule from these projections. The quality of the reconstruction eventually hinges on the quality of the particle picking stage. Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.

@@

The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
%
Despite this progress, detecting small molecules in the micrographs remains a challenge.
We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules. Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability. \TODO{Need a ref for this claim.}

@@

As a proof of concept, we study a simplified model for 3-D reconstruction directly from the micrograph on a simulated data. 
In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the volume.
For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and the latter are separated in the micrograph. Importantly, there is no need to detect the projections. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the volume. To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares. In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details. 
%As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details. 
\TODO{Do we want to stress that we get only low-resolution of the volume?}

@@

% while neglecting important aspects as discussed in detail in TKTK.

%In first model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
%The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably. This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}. We study it in more details in a companion paper~\cite{bendory2018estimation}. An extension to multiple planted images is analyzed in~\cite{bendory2018estimation}.
%
%In the second model, we consider the 3-D reconstruction problem as it appears in cryo-EM, \TODO{Here we need to elaborate a bit.} This is the main result of this paper. \TODO{We probably need to switch the order of this paragraph.}

%A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure. Instead, we solve a simpler problem that we believe captures key elements of the SPR problem. We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.

%In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume.
%For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the projections are well separated and we acquire enough of them. Importantly, there is no need to detect the projections. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the volume. To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares. 
%We use similar technique for the simpler model of planted image as illustrated in Figure~\ref{fig:Einst_example}.

@@

\begin{figure}[t]
	\centering
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
		\caption{$\sigma = 0$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
		\caption{$\sigma = 0.5$}
	\end{subfigure}
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
		\caption{$\sigma = 3$}
	\end{subfigure}
	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$. Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein. In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image. In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known. By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done. \TODO{Do we want to replace with a cryo-EM figure? This figure will be positioned with the rest of the figures about Einstein's example}}	
\end{figure}

\section{Results} \label{sec:results}

@@

\section{Methods} \label{sec:methods}

\subsection{Toy 2-D experiment}

>>>>

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a]{Tamir Bendory}
\author[b]{Nicolas Boumal} 
\author[c]{William Leeb}
\author[a]{Eitan Levin}
\author[a,b]{Amit Singer}

\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
\affil[c]{School of Mathematics, University of
	Minnesota, Minneapolis, MN, USA }

% Please give the surname of the lead author for the running footer
\leadauthor{Bendory}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

@@

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

\dropcap{C}ryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise}
In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. Within the ice, the molecules are randomly oriented and positioned. The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}. Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions. The goal is to construct 3-D models of the molecules from the micrographs.

@@

All contemporary methods in the field split the reconstruction procedure into several stages.
The first stage consists in extracting the various particle projections from the micrographs. This stage is called \emph{particle picking}. Later stages aim to construct a 3-D model of the molecule from these projections. The quality of the reconstruction eventually hinges on the quality of the particle picking stage. Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.

@@

The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
Despite this progress, detecting small molecules in the micrographs remains a challenge.
We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules. Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability. \TODO{Need a ref for this claim.}

@@

As a proof of concept, we study a simplified model for 3-D reconstruction directly from the micrograph on a simulated data. 
In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the volume.
For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and the latter are separated in the micrograph. Importantly, there is no need to detect the projections. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the volume. To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares. In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details. 
\TODO{Do we want to stress that we get only low-resolution of the volume?}

@@

@@

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
		\caption{$\sigma = 0$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
		\caption{$\sigma = 0.5$}
	\end{subfigure}
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
		\caption{$\sigma = 3$}
	\end{subfigure}
	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$. Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein. In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image. In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known. By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done. \TODO{Do we want to replace with a cryo-EM figure? This figure will be positioned with the rest of the figures about Einstein's example}}	
\end{figure*}

\section{Proof of concept: A mathematical toy model}

Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data. Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
\begin{align}
y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
\label{eq:model}
\end{align}
where $\ast$ denotes linear convolution. 
While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem. As will be shown next, in the low signal-to-noise ratio (SNR) environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.

The binary signals obey the following property:
\begin{align}
\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
\label{eq:spacing}
\end{align}
In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.

\subsection{Related work}

For $K=1$, our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
%
\begin{math}
%
y = x\ast w + \varepsilon,  
%
\end{math} 
%
where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}. In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$). The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.

Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$. For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods). If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.

Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}. Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}. Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.

In special cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}. The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}. However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets. 
Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total. Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large. However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.

\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}

Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification. Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.

\section{Autocorrelation analysis}

In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{align}
a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
Explicitly, the first-, second- and third-order autocorrelations are given by
\begin{align} 
a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
\begin{align*}
a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
\end{align*}
%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.

For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first. It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
\begin{align}
\gamma & = \frac{M L}{N}
\end{align}
denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$. Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$. The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
\begin{align*}
\E\{ a_y^1 \} & = \gamma a_x^1.
\end{align*}
We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
\begin{align*}
\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
\end{align*}
Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)

The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations. Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries. Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence. As a result,
\begin{align*}
\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell]
\end{align*}
for $\ell = 0, \ldots, L-1$, where $\ell$ denotes the Kronecker delta function. The last part captures the autocorrelation of the noise. Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
Along the same lines, one can establish a relation for third-order autocorrelations:
\begin{align}
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\ell[\ell_1,0]+\ell[0,\ell_2]+\ell[\ell_1,\ell_2]\big),
\label{eq:data_ac_k1}
\end{align}
for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.

\section{Theory} \label{sec:theory}

If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible. We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
%
%To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$. Suppose too that the oracle provides us with $x$ itself. That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations. This is an easier problem than detecting the support of $s$. Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}. Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.

%\TODO{Here we should give the Will's proposition for the impossibility of detection}

Therefor, we need to consider a different approach. In this paper, we consider autocorrelation analysis. In what follows, we present several results on properties of autocorrelations. For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.

A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
%
\begin{align} \label{eq-uniqueness}
%
z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
%
\end{align}

In particular, we have proven the following proposition:

\begin{proposition} \label{prop:uniqueness}
	%
	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
\end{proposition}

Some remarks are in order. First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0. In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.

Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
%%%and therefore the assumption that the first and last entries are nonzero is met.
In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.

\begin{comment}

%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime. Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.

First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity. In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}. 
Second, these results carry through to signals of any dimension.
Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime. Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.

, this uniqueness result holds for signals of any dimension. Third

Furthermore,
as proven in the following simple proposition.
%
\begin{proposition} \label{prop:uniqueness}
%
Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$. More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \ell>0$.
Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\ell}$.

\end{proposition}

\begin{proof}
%
By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
%
\begin{equation*}
%
a_z^3[k,L-1] = z[0]z[k]z[L-1].
%
\end{equation*}
%
In addition, 
%
\begin{equation*}
%
\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\ell}.
%
\end{equation*} 
%
\end{proof}

A few remarks are in order. 
First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity. In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}. 
Second, these results carry through to signals of any dimension.
Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime. Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.

\end{comment}

Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations. Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}. The sign ambiguity can be resolved by the mean of the signal if it is not zero. However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.

The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$. We will show, however, that $x$ is still identifiable from the observed moments of $y$. In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.

First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
%
\begin{proposition} \label{prop:gamma}
	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
	%
	\begin{equation*}
	%
	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
	%
	\end{equation*}
	%
\end{proposition}
\begin{proof}
	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
\end{proof}

Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable. For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.

\begin{proposition} \label{prop:gamma_sigma}
	%
	Let $K=1$, and $\sigma > 0$ be fixed. Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$. If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean. 
	\begin{proof}
		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
	\end{proof}
\end{proposition}

From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
\begin{corollary}
	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
	\begin{itemize}
		\item Either the signal $x$ is generic; or
		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
	\end{itemize}
\end{corollary}

@@

% Bibliography
\bibliography{ref}

\section{Numerical experimets details}

\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}

Throughout the proof, we consider the case of one signal $K=1$. The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
